\TheTitle

### 2017-06-29 paper/methodology.tex
Methodology: Analysis Section
Adding some information on the analysis.

% TODO: Show this in the introduction maybe
% It is worth noting that in the fourth
% quartile, the size of the tree drops off quickly from the top tree, with
% the next tree containing only 4708 nodes, and the third largest tree
% containing only 2349 commits.

% TODO: Fix this, the commit hash is wrong.
Using this technique, we selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), which we will refer to as
\comA, and commit \emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from
the tree containing seven nodes (Figure~\ref{fig:commit_2}), which we
will refer to as \comB.

@@

The answers to each question is relatively straight-forward, as we can
extract the information directly from gitk and Linvis. Measuring the
accuracy of the questions is more challenging. In the question regarding
the merges leading to the merging of a given commit, both the merges and
the ordering of the merges matter.

@@

>>>>

% TODO: Show this paragraph in the introduction
% It is worth noting that in the fourth
% quartile, the size of the tree drops off quickly from the top tree, with
% the next tree containing only 4708 nodes, and the third largest tree
% containing only 2349 commits.

Using this technique, we selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), which we will refer to as
\comA, and commit \emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from
the tree containing seven nodes (Figure~\ref{fig:commit_2}), which we
will refer to as \comB.

@@

The answers to each question is relatively straight-forward, as we can
extract the information directly from gitk and Linvis. Measuring the
accuracy of the questions is more challenging. In the question regarding
the merges leading to the merging of a given commit, both the merges and
the ordering of the merges matter. In the cases where the answer is not
a numerical value, we use the edit distance to determine the accuracy of
an answer. An edit distance of zero indicates a correct answer, while
any number other than zero indicates an incorrect answer. Adding,
reordering (where important), and removing commits or merges all incur a
penalty of 1 added to the edit distance.

@@

The information is then inserted into a sql database for further
analysis.

\subsection{Analysis}

As the goals of each section are different, the techniques for analyzing
the results are different. The conceptual questions are to demonstrate
the difficulty in comprehending the DAG model, so we simply provide the
metrics, showing how well the participants did in answering the
questions asked. The summarization tasks are meant for comparing the
ability of the participants to summarize two commits from the Linux
repository. As this is a comparison, further analysis is necessary to
determine the significance of our results. The final portion of the
study is designed to help us understand the group of users that we are
working with.

As the goals of the conceptual questions are to demonstrate the
difficulty in comprehending the DAG model, and determine how closely
users are able to make the mapping from the DAG to showing how a commit
was merged into the master branch, no further statistical analysis will
be performed on this data. We will provide the metrics response,
accuracy, and time metrics for these questions. No comparisons are made
between the models in these tasks, so no further analysis is necessary.

The summarization tasks are designed to compare the two models when the
participant is summarizing various aspects of the repository, including
the files modified and authorship information. We will use three terms
to describe the performance of a user; correctness, which indicates
simply whether the participant was correct or not, making no indication
toward how far from the correct answer they were; accuracy, indicating
how far from the correct answer the participant was; timing, which
indicates how long a participant took to answer the question. We begin
the analysis of these questions using the McNemar test, with $\alpha =
0.005$, measuring the correctness of the results provided by the
participant when using \tool versus gitk.
% TODO: cite the McNemar test maybe?
If the McNemar test indicates that we do not reject the null hypothesis,
we continue analyzing the difference in accuracy and timing metrics for
the merge-tree model versus the DAG.

For each test, we use a confidence level $\alpha = 0.005$, resulting in
a $\chi^2$ test statistic of 7.879.

% TODO: Add the null hypothesis and type of metrics analyzed for each summarization question
